---
title: "hm4stat632"
author: "Jessica Grover"
date: "3/18/2022"
output:
  word_document: default
  pdf_document: default
---

#a.
```{r}
library(MASS)
attach(Boston)
```
```{r}
Y <- matrix(medv, ncol=1)
```
This is response vector

Let us now design a matrix
```{r}
X <- cbind(Intercept = 1, dis, rm, tax, chas)
X <- as.matrix(X)
X[1:4,]

```

Manually calculating mean square estimates
```{r}
(betaHat <- solve(t(X) %*% X) %*% t(X) %*% Y)

```

Comparing with lm()
```{r}
lmBoston <- lm(medv ~ dis + rm + tax + chas, data=Boston)
coef(lmBoston)
```

We can conclude that results are same as the parameter estimates provided by the lm() function.

#b.
```{r}
n <- nrow(Boston)
p <- 4
resid <- as.numeric(Y - X %*% betaHat)
sigmaHat2 <- sum(resid^2) / (n-p-1)
covBetaHat <- sigmaHat2 * solve(t(X) %*% X)
covBetaHat
```
```{r}
seBetaHat <- sqrt(diag(covBetaHat))
seBetaHat
```
#Comparing with lm()
```{r}
summary(lmBoston)$coef
```

```{r}
vcov(lmBoston)

```
```{r}
summary(lmBoston)$coef[,2]

```
After checking we got that the square root of the diagonal entries of this matrix are the same as the standard errors provided by the lm() function.


